Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-05-30 PaperLatex/paper.tex
Working on benchmarks, minor edits to paper

\paragraph{Optimizing parameters.}
"xolotl" can use the Global Optimization and Parallel Computing toolboxes for "MATLAB" to optimize network parameters.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		TECHNICAL DETAILS
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Details}

\subsection{Benchmarking}

@@

>>>>

\paragraph{Optimizing parameters.}
"xolotl" can use the Global Optimization toolbox for "MATLAB" to optimize any accessible "xolotl" parameters. The toolbox is algorithm-agnostic and accepts any function in "MATLAB" with a scalar first output as the objective function. Simulations run on multi-core processors or high-performance computing clusters using the Parallel Computing toolbox.

@@

The focus on ease-of-use and speed means some features were elided in the streamlining process.

\paragraph{Reliance on compiled \texttt{C++} code.} While "MATLAB" comes with robust features for compiling "C" and "C++" code, "xolotl" cannot run without "C++" compilation. For users, this necessitates the additional step of setting up the "mex" compiler which can be problematical, especially for nonstandard (e.g. Arch-based Linux). Secondly, compilation adds a small amount to total processing time. Longer simulations ($>1000$ time-steps) minimizes this effect. Adding new conductances also requires writing some "C++" code. For model conductances in the Hodgkin-Huxley formalism \autocite{hodgkinMeasurementCurrentvoltageRelations1952, dayanTheoreticalNeuroscience2001}, adjustments consist of changing default values in a template "C++" header file. Implementing a new integration scheme requires much more in-depth usage of "C++".

\paragraph{Limited to conductance-based models.} "xolotl" has been developed specifically for conductance-based models. It does not currently support current-based models.

\paragraph{Limited numerical integration strategies.} While the exponential Euler method performs well in neuronal models \autocite{ohErrorAnalysisSpecialized2006, dayanTheoreticalNeuroscience2001}, it may be desirable to use other methods under certain conditions. "xolotl" does not currently support other integration schemes for its build-in conductances, nor does the software support error-sensitive variable step-sizes.

\paragraph{Inefficient tools for handling large networks.} While "xolotl" can integrate large networks ($>1000$ compartments), the tools used to index, label, hash, and search large networks become prohibitively slow. "xolotl" uses string-based comprehension for labeling compartments, which is suited to descriptively-named compartments, but computationally slow for searching and indexing.

@@

@@

"xolotl" fosters reproducibility in science. While the availability of hosting sites with version control such as GitHub and GitLab

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		PUBLICATION DETAILS
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
